---
title: "H#7"
author: "Jasmine Shrestha"
date: "2023-07-01"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("/Users/student/Downloads")
```

## (a) Reading the raw data into R

```{r}
wb_data <- read.csv("WorldBankData.csv")
wb_data
```
## (b) Filtering the rows for the indicator of "Government expenditure on education, total (% of GDP)

```{r}
library(dplyr)
library(tidyr)
wb_data1 = filter(wb_data, Indicator.Name == 'Government expenditure on education, total (% of GDP)')
wb_data1
```


## (b) To visually compare expenditures for 1990 and 2014

```{r}
library(ggplot2)
ggplot(wb_data1, aes(x = Country.Name, y = X1990, fill = X2014, las = 2)) +
    geom_col() 
```

## (c) Next, we visually compare how the expenditure across all years varies for a given country. Use the gather() function to gather the year columns together.

```{r}
library(tidyr)
long_year_data = wb_data1 %>%
gather(key = year,
       value=value,
       X1960:X)
long_year_data
```

## (c) Display the first 20 rows of the new data frame. 

```{r}
head(long_year_data, 20)
```

## (c) Visualize government expenditure on education, total (% of GDP), for China and USA. You should two lines on the same graph. 

```{r}
library(ggplot2)

long_year_data$year <- as.numeric(substr(long_year_data$year, 2, nchar(long_year_data$year)))

wb_dataf <- long_year_data %>% filter(Indicator.Name == 'Government expenditure on education, total (% of GDP)') 

filtered_data <- wb_dataf %>%
  filter(Country.Name %in% c("China", "United States"))

ggplot(filtered_data, aes(x = year, y = value, color = Country.Name)) +
  geom_line() +
  labs(x = "Year", y = "Government Expenditure on Education (% of GDP)") +
  ggtitle("Government Expenditure on Education, Total (% of GDP) for China and USA")
```

## (d) You may want to assess the relationship between each country's literacy rate (a first indicator) and its unemployment rate (a second indicator). Do it for year 2014. Summarize your findings.

```{r}
library(tidyr)
lit_unemp = wb_data %>%
gather(key = year,
       value=value,
       X2014:X)
lit_unemp
```

```{r}
lit_unemp$year <- as.numeric(substr(lit_unemp$year, 2, nchar(lit_unemp$year)))

# Filter the literacy and unemployment data for year 2014
literacy_2014 <- subset(lit_unemp, year == 2014 & Indicator.Name == "Literacy rate, adult total (% of people ages 15 and above)")

unemployment_2014 <- subset(lit_unemp, year == 2014 & Indicator.Name == "Unemployment, total (% of total labor force) (modeled ILO estimate)")

# Plot the relationship between literacy rate and unemployment rate for year 2014
plot(literacy_2014$value, unemployment_2014$value, xlab = "Literacy Rate", ylab = "Unemployment Rate", main = "Relationship between Literacy Rate and Unemployment Rate (2014)")

```



