---
title: "Lists, Data Frames and Basic Plots"
author: "Jasmine Shrestha"
date: "2023-06-05"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section One

### To create a List

```{r}
Create_list <- list(mtcars,iris,USArrests)
Create_list
```

### To create a named list

```{r}
Named_list <- list(df1 = mtcars, df2 = iris, df3 = USArrests)
Named_list
```

### To access Species column in df2

```{r}
access_species <- Named_list[[2]][,5]
access_species
```
```{r}
```{r}
access_species <- Named_list$df2[,5]
access_species
```
```{r}
paste(iris$Species)
```


## Section Two

qplot: qplot is intended to be similar to base r plot() function, trying to always plot out your data without requiring too
much specifications.

### To create a scatter plot of Sepal.Length vs Sepal.Width based on the iris data frame

```{r}
library(ggplot2)
qplot(x = Sepal.Width, y = Sepal.Length, data = iris)
```

### To create a scatter plot of Sepal.Length vs Sepal.Width, coloring the points by the Species
```{r}
qplot(x = Sepal.Width, y = Sepal.Length, col = Species, data = iris)
```

### To create a scatter plot of disp vs mpg, coloring the points by am. The variables are from the mtcars data frame. 
```{r}
mtcars_data <- mtcars
mtcars_data$am <- as.factor(mtcars_data$am)
qplot (x = disp, y = mpg, col = am, data = mtcars_data)
```

