---
title: "H#9"
author: "Jasmine Shrestha"
date: "2023-07-19"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("/Users/student/Downloads")
```

## (a) Reading the raw data into R

```{r}
ccr_data <- read.csv("Customer-Churn-Records.csv")
ccr_data
```

## Creating summary table for CreditScore and Geography  
```{r}
credscore <- aggregate(ccr_data$CreditScore, list(ccr_data$Geography), FUN=mean)
credscore
```

## Creating barplot for CreditScore summary table
```{r}
barplot(credscore$x, names = credscore$Group.1, main = "Average credit score of customers in each geographical region")
```


## Creating summary table for Age and Geography  
```{r}
age <- aggregate(ccr_data$Age, list(ccr_data$Geography), FUN=mean)
age
```

## Creating barplot for Age summary table
```{r}
barplot(age$x, names = age$Group.1, main = "Average age of customers in each geographical region")
```

## Creating summary table for Tenure and Geography  
```{r}
tenure <- aggregate(ccr_data$Tenure, list(ccr_data$Geography), FUN=mean)
tenure
```

## Creating barplot for Tenure summary table
```{r}
barplot(tenure$x, names = tenure$Group.1, main = "Average tenure of customers in each geographical region")
```

## Creating summary table for Balance and Geography  
```{r}
bal <- aggregate(ccr_data$Balance, list(ccr_data$Geography), FUN=mean)
bal
```

## Creating barplot for Balance summary table
```{r}
barplot(bal$x, names = bal$Group.1, main = "Average balance of customers in each geographical region")
```

## Creating summary table for Number of Products and Geography  
```{r}
products <- aggregate(ccr_data$NumOfProducts, list(ccr_data$Geography), FUN=mean)
products
```

## Creating barplot for Products summary table
```{r}
barplot(products$x, names = products$Group.1, main = "Average products of customers in each geographical region")
```

## Creating summary table for HasCrCard and Geography  
```{r}
crcard <- aggregate(ccr_data$HasCrCard, list(ccr_data$Geography), FUN=mean)
crcard
```

## Creating barplot for CreditScore summary table
```{r}
barplot(crcard$x, names = crcard$Group.1, main = "Average percentage of customers having credit card in each geographical region")
```

## Creating summary table for IsActiveMember and Geography  
```{r}
active <- aggregate(ccr_data$IsActiveMember, list(ccr_data$Geography), FUN=mean)
active
```

## Creating barplot for IsActiveMember summary table
```{r}
barplot(active$x, names = active$Group.1, main = "Average percentage of active customers in each geographical region")
```

## Creating summary table for EstimatedSalary and Geography  
```{r}
salary <- aggregate(ccr_data$EstimatedSalary, list(ccr_data$Geography), FUN=mean)
salary
```

## Creating barplot for Estimated Salary summary table
```{r}
barplot(salary$x, names = salary$Group.1, main = "Average estimated salary of customers in each geographical region")
```

## Creating summary table for Exited and Geography  
```{r}
exit <- aggregate(ccr_data$Exited, list(ccr_data$Geography), FUN=mean)
exit
```

## Creating barplot for exited summary table
```{r}
barplot(exit$x, names = exit$Group.1, main = "Average percentage of customers exitting in each geographical region")
```

## Creating summary table for Complain and Geography  
```{r}
complains <- aggregate(ccr_data$Complain, list(ccr_data$Geography), FUN=mean)
complains
```

## Creating barplot for complain summary table
```{r}
barplot(complains$x, names = complains$Group.1, main = "Average percentage of customers complaining in each geographical region")
```

## Creating summary table for Satisfaction.Score and Geography  
```{r}
satisfaction <- aggregate(ccr_data$Satisfaction.Score, list(ccr_data$Geography), FUN=mean)
satisfaction
```

## Creating barplot for Satisfaction.Score summary table
```{r}
barplot(satisfaction$x, names = satisfaction$Group.1, main = "Average satisfaction score of customers in each geographical region")
```

## Creating summary table for Point.Earned and Geography  
```{r}
point <- aggregate(ccr_data$Point.Earned, list(ccr_data$Geography), FUN=mean)
point
```

## Creating barplot for Point Earned summary table
```{r}
barplot(point$x, names = point$Group.1, main = "Average points of customers in each geographical region")
```



